---
output:
  pdf_document: default
---

<!-- Kommentare sind moeglich mit HTML Kommentaren
<!-- Based on knitr-minimal.Rmd on http://yihui.name/knitr/demo/minimal/ -->

# MRI-Together 2021-https://mritogether.github.io/

## A White Hat’s Guide to p-Hacking

### Dr. Xeni Deligianni- University of Basel
xeni.deligianni@unibas.ch
https://github.com/XDeligianni

Imagine, we have two data distributions, one the **controls** and one a distribution that we want to compare to the controls.
This could be the quantitative values of a volunteers' group (controls="ctrl"), let's call them **qmr** and
the respective values of a different group e.g. patients ("pat") with a certain condition.

Let's assume for now that the distributions are **normal** Gaussian distributions. 
So let's assume we checked the distributions and that BEFORE starting our analysis, we have a **hypothesis** that in disease presence qmr values are increased.
And let's imagine we have estimated that we should measure and we measured under identical and ideal conditions **nr_s healthy controls** and **nr_s patients**.

## Let' s agree on some definitions first

**$\alpha$**: Significance level.

**p-value**:the probability of obtaining the observed difference, or one more extreme, if the null hypothesis is true. A p-value below **$\alpha$** will lead to the null hypothesis being rejected.

## Ready? Let's create some fictional data. 

Let's create two perfectly **normal distributions**. One with **mean** 40 and **standard deviation** (sd) 5 and one with mean 10 and standard deviation 2. 
And let's visualize at their distributions, as well as the distribution of their difference.
We start with 1000 samples for each ditribution.

```{r echo= FALSE}
library(ggplot2)# A great library for visualization
library(viridis)#colorblind accessible

#set.seed(2)#example, has to be set to produce same random distributions
#qmr <-c(rnorm(1000, mean=10, sd=5),rnorm(1000, mean=40, sd=5))
#qmr<-c(qmr,qmr[1001:2000]-qmr[1:1000])
load('New_Data.RData')
subj <- as.factor(c(rep("ctrl",1000),rep("pat",1000),rep("diff",1000)))
d.exp <- data.frame(qmr,subj)

x_p<-d.exp[d.exp$subj=='pat',]$qmr
bw_p <- 2 * IQR(x_p) / length(x_p)^(1/3)#decide for the nr of bins-Friedman-Diaconis rule
x_c<-d.exp[d.exp$subj=='ctrl',]$qmr
bw_c <- 2 * IQR(x_c) / length(x_c)^(1/3)#decide for the nr of bins-Friedman-Diaconis rule

ggplot(d.exp,aes(x=qmr,fill =subj)) + 
  geom_histogram(binwidth = 1,alpha=0.5,position='identity')+scale_fill_viridis_d()

```



## That looks clear. Doesn't it? Let's also look at the boxplot visualization.

```{r echo = FALSE}
library(ggplot2)# A great library for visualization
library(viridis)
load('New_Data.RData')
##set.seed(2)
#qmr <-c(rnorm(1000, mean=10, sd=5),rnorm(1000, mean=40, sd=5))
#subj <- c(rep("ctrl",1000),rep("pat",1000),rep("diff",1000))
#d.exp <- data.frame(qmr,subj)
x<-d.exp[d.exp$subj=='pat',]$qmr
bw <- 2 * IQR(x) / length(x)^(1/3)#decide for the nr of bins-Friedman-Diaconis rule
ggplot(data = d.exp,mapping = aes(y = qmr,x = subj, fill=subj)) + geom_boxplot()+scale_fill_viridis_d()
#colorblind accessible colors

```

## So what's next? Whar result would we get from a t-test?

What would we get by testing whether there is a difference in these 2 distributions and if the difference is different than zero.
And let's see what would happen if we wouldn't have 1000 samples for each distribution, but less. 
Try to change the nr_s and plot. 

```{r echo = FALSE}
load('New_Data.RData')
#set.seed(2)
#qmr <-c(rnorm(1000, mean=10, sd=5),rnorm(1000, mean=40, sd=5))
#subj <- c(rep("ctrl",1000),rep("pat",1000),rep("diff",1000))
#d.exp <- data.frame(qmr,subj)
# Randomly choose number of samples (1000/50/25/15/5)

nr_s<-4

p_series<-vector()
for (i in 1:100) {
  sample_rows_ctrl<-sample(nrow(d.exp[d.exp$subj=="ctrl",]),nr_s)
  sample_rows_pat<-1000+sample(nrow(d.exp[d.exp$subj=="pat",]),nr_s)
  d.exp_sub<-rbind(d.exp[sample_rows_ctrl,],d.exp[sample_rows_pat,])
  p_Res<-t.test(d.exp_sub[d.exp_sub$subj=="pat",]$qmr, d.exp_sub[d.exp_sub$subj=="ctrl",]$qmr, paired = FALSE,
alternative = "two.sided", conf.level = 0.95,var.equal=TRUE)
  p_series [i]<-p_Res$p.value
}
plot(p_series,ylim=c(0,0.06))
abline(h=0.05)

```

###So let's sum up and continue

```{r echo= FALSE}
library(ggplot2)# A great library for visualization
library(viridis)
library(ggpubr)
load('New_Data_sub.RData')

####### Histograms
x_p<-d.exp_sub[d.exp_sub$subj=='pat',]$qmr
bw_p <- 2 * IQR(x) / length(x)^(1/3)#decide for the nr of bins-Friedman-Diaconis rule
x_c<-d.exp_sub[d.exp_sub$subj=='ctrl',]$qmr
bw_c <- 2 * IQR(x) / length(x)^(1/3)#decide for the nr of bins-Friedman-Diaconis rule

####### Histograms
a<-ggplot(d.exp_sub,aes(x=qmr,fill =subj)) + 
  geom_histogram(binwidth = bw_p,alpha=0.5,position='identity')+scale_fill_viridis_d()
b<-ggplot(d.exp_sub[d.exp_sub$subj=="diff",],aes(x=qmr,fill =subj)) + 
  geom_histogram(binwidth = bw_p,alpha=0.5,position='identity')+scale_fill_viridis_d()
####### Boxplots
c<-ggplot(data = d.exp_sub,mapping = aes(y = qmr,x = subj, fill=subj)) + geom_boxplot()+scale_fill_viridis_d()

ggarrange(a, b,c, labels = c("A","B","C"),
                    ncol = 2, nrow = 2)
#### t-test
t.test(d.exp_sub[d.exp_sub$subj=="pat",]$qmr, d.exp_sub[d.exp_sub$subj=="ctrl",]$qmr, paired = TRUE,
alternative = "two.sided", conf.level = 0.95,var.equal=TRUE)
```
### But what if we don't have 1000 samples or 1000 representative samples?

## **Trap Nr. 1**: Be real! 5 data points is not 5000
Topic 1: The number of samples is important
What if we have 15 samples of some less different data. Let's get them & repeat the steps

p-values change but our difference is still constantly higher than 0. 
## But what if things are not so clear?
Let's modify bring the mean values closer and increase the standard deviation.
Keeping the assumptions for t-test we keep standard deviation the same.

```{r echo= FALSE}
library(ggplot2)# A great library for visualization
library(viridis)
library(ggpubr)
library(effsize)
# Randomly choose number of samples (1000/50/25/15/5) 
nr_s<-5#TRY TO CHANGE THIS NUMBER
#Later you can also go ahead and modify the mean values and study the effect
set.seed(1000)
qmr <-c(rnorm(nr_s, mean=25.5, sd=10),rnorm(nr_s, mean=34.2, sd=10))
qmr<-c(qmr,qmr[1:nr_s]-qmr[(nr_s+1):(2*nr_s)])
subj <- c(rep('ctrl',nr_s),rep('pat',nr_s),rep("diff",nr_s))
d.exp <- data.frame(qmr,subj)
####### Histograms
x_p<-d.exp[d.exp$subj=='pat',]$qmr
bw_p <- 2 * IQR(x_p) / length(x_p)^(1/3)#decide for the nr of bins-Friedman-Diaconis rule
x_c<-d.exp[d.exp$subj=='ctrl',]$qmr
bw_c <- 2 * IQR(x_c) / length(x_c)^(1/3)#decide for the nr of bins-Friedman-Diaconis rule

####### Histograms
a<-ggplot(d.exp,aes(x=qmr,fill =subj)) + 
  geom_histogram(binwidth = 3,alpha=0.5,position='identity')+scale_fill_viridis_d()
b<-ggplot(d.exp[d.exp$subj=="diff",],aes(x=qmr,fill =subj)) + 
  geom_histogram(binwidth = 3,alpha=0.5,position='identity')+scale_fill_viridis_d()
####### Boxplots
c<-ggplot(data = d.exp,mapping = aes(y = qmr,x = subj, fill=subj)) + geom_boxplot()+scale_fill_viridis_d()+geom_point()

ggarrange(a, b,c, labels = c("A","B","C"),
                    ncol = 2, nrow = 2)
#### t-test
t.test(d.exp[d.exp$subj=="pat",]$qmr, d.exp[d.exp$subj=="ctrl",]$qmr, paired = TRUE,
alternative = "two.sided", conf.level = 0.95,var.equal=TRUE)

cohen.d(d.exp[d.exp$subj=="pat",]$qmr, d.exp[d.exp$subj=="ctrl",]$qmr)
```
```{r echo= FALSE}
library(effsize)
load('Difficult_Data.RData')
nr_s<-5

p_series<-vector()
cohenD<-vector()
for (i in 1:500) {
  sample_rows_ctrl<-sample(nrow(d.exp[d.exp$subj=="ctrl",]),nr_s)
  sample_rows_pat<-1000+sample(nrow(d.exp[d.exp$subj=="pat",]),nr_s)
  d.exp_sub<-rbind(d.exp[sample_rows_ctrl,],d.exp[sample_rows_pat,])
  p_Res<-t.test(d.exp_sub[d.exp_sub$subj=="pat",]$qmr, d.exp_sub[d.exp_sub$subj=="ctrl",]$qmr, paired = TRUE,
alternative = "two.sided", conf.level = 0.95,var.equal=TRUE)
  rcohen<-cohen.d(d.exp_sub[d.exp_sub$subj=="pat",]$qmr, d.exp_sub[d.exp_sub$subj=="ctrl",]$qmr)
  p_series [i]<-p_Res$p.value
  cohenD[i]<-rcohen$estimate
}
par(mfrow=c(2,2))
plot(p_series,ylim=c(0,1))
abline(h=0.05,col="red")
hist(p_series,breaks=30)
abline(v=0.05,col="red")
plot(cohenD)

```
### What can we do?

Decide in advance the sample size we need! If we don' t know maybe it is an exploratory analysis after all

###Clinical vs statistical significance (to the slides and back)

## **Trap Nr. 2**: Step 1: Look at your data

### Not all datasets are normal, t-test is not for everything!
The same way as mean is not always the proper statistic.

```{r echo= FALSE}
library(ggplot2)# A great library for visualization
library(viridis)
library(ggpubr)
library(effsize)
# Randomly choose 50/25/15/5 samples
nr_s<-1000
# Generate a random negative binomial distribution
qmr <-c(15+250*rexp(1000,25),35-250*rexp(1000,25))
qmr<-c(qmr,qmr[1:nr_s]-qmr[(nr_s+1):(2*nr_s)])
subj <- c(rep('ctrl',nr_s),rep('pat',nr_s),rep("diff",nr_s))
d.exp <- data.frame(qmr,subj)
####### Histograms
x_p<-d.exp[d.exp$subj=='pat',]$qmr
bw_p <- 2 * IQR(x_p) / length(x_p)^(1/3)#decide for the nr of bins-Friedman-Diaconis rule
x_c<-d.exp[d.exp$subj=='ctrl',]$qmr
bw_c <- 2 * IQR(x_c) / length(x_c)^(1/3)#decide for the nr of bins-Friedman-Diaconis rule

####### Histograms
a<-ggplot(d.exp,aes(x=qmr,fill =subj)) + 
  geom_histogram(alpha=0.5,position='identity')+scale_fill_viridis_d()
b<-ggplot(d.exp[d.exp$subj=="diff",],aes(x=qmr,fill =subj)) + 
  geom_histogram(alpha=0.5,position='identity')+scale_fill_viridis_d()
####### Boxplots
c<-ggplot(data = d.exp,mapping = aes(y = qmr,x = subj, fill=subj)) + geom_boxplot()+scale_fill_viridis_d()+geom_point()

ggarrange(a, b,c, labels = c("A","B","C"),
                    ncol = 2, nrow = 2)
#### t-test
t.test(d.exp[d.exp$subj=="pat",]$qmr, d.exp[d.exp$subj=="ctrl",]$qmr, paired = TRUE,
alternative = "two.sided", conf.level = 0.95)
wilcox.test(d.exp[d.exp$subj=="pat",]$qmr, d.exp[d.exp$subj=="ctrl",]$qmr, paired = TRUE,alternative = "two.sided")

```



```{r echo= FALSE}
library(ggplot2)# A great library for visualization
library(viridis)
library(ggpubr)
library(effsize)
# Randomly choose number of samples (1000/50/25/15/5) 
nr_s<-10
#Later you can also go ahead and modify the mean values and study the effect
qmr <-c(rnorm(nr_s, mean=25, sd=8),rnorm(nr_s, mean=35, sd=8))
qmr<-c(qmr,qmr[1:nr_s]-qmr[(nr_s+1):(2*nr_s)])
subj <- c(rep('ctrl',nr_s),rep('pat',nr_s),rep("diff",nr_s))
d.exp <- data.frame(qmr,subj)
####### Histograms
x_p<-d.exp[d.exp$subj=='pat',]$qmr
bw_p <- 2 * IQR(x_p) / length(x_p)^(1/3)#decide for the nr of bins-Friedman-Diaconis rule
x_c<-d.exp[d.exp$subj=='ctrl',]$qmr
bw_c <- 2 * IQR(x_c) / length(x_c)^(1/3)#decide for the nr of bins-Friedman-Diaconis rule

####### Histograms
a<-ggplot(d.exp,aes(x=qmr,fill =subj)) + 
  geom_histogram(binwidth = 3,alpha=0.5,position='identity')+scale_fill_viridis_d()
b<-ggplot(d.exp[d.exp$subj=="diff",],aes(x=qmr,fill =subj)) + 
  geom_histogram(binwidth = 3,alpha=0.5,position='identity')+scale_fill_viridis_d()
####### Boxplots
c<-ggplot(data = d.exp,mapping = aes(y = qmr,x = subj, fill=subj)) + geom_boxplot()+scale_fill_viridis_d()+geom_point()

ggarrange(a, b,c, labels = c("A","B","C"),
                    ncol = 2, nrow = 2)
#### t-test
t.test(d.exp[d.exp$subj=="pat",]$qmr, d.exp[d.exp$subj=="ctrl",]$qmr, paired = TRUE,
alternative = "two.sided", conf.level = 0.95,var.equal=TRUE)

cohen.d(d.exp[d.exp$subj=="pat",]$qmr, d.exp[d.exp$subj=="ctrl",]$qmr)
```

```{r echo= FALSE}
load('Not_normal_Distr.RData')
nr_s<-4

p_series<-vector()
cohenD<-vector()
for (i in 1:500) {
  sample_rows_ctrl<-sample(nrow(d.exp[d.exp$subj=="ctrl",]),nr_s)
  sample_rows_pat<-1000+sample(nrow(d.exp[d.exp$subj=="pat",]),nr_s)
  d.exp_sub<-rbind(d.exp[sample_rows_ctrl,],d.exp[sample_rows_pat,])
  p_Res<-t.test(d.exp_sub[d.exp_sub$subj=="pat",]$qmr, d.exp_sub[d.exp_sub$subj=="ctrl",]$qmr, paired = FALSE,
alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
  rcohen<-cohen.d(d.exp_sub[d.exp_sub$subj=="pat",]$qmr, d.exp_sub[d.exp_sub$subj=="ctrl",]$qmr)
  p_series [i]<-p_Res$p.value
  cohenD[i]<-rcohen$estimate
}
par(mfrow=c(2,2))
plot(p_series,ylim=c(0,1))
abline(h=0.05,col="red")
hist(p_series,breaks=30)
abline(v=0.05,col="red")
plot(cohenD)


```
### Trap 3: Just one more experiment then!It almost looks good. Let's repeat it. Trap of adding data on marginal distributions. 
```{r echo= FALSE}
load('Adding_values.RData')
d.extra<-d.exp_s

d.exp_w_Points<-rbind(d.exp_limit,data.frame(qmr=18,subj="ctrl"),data.frame(qmr=40,subj="pat"))

a<-ggplot(d.exp_w_Points,aes(x=qmr,fill =subj)) + 
  geom_histogram(binwidth = 3,alpha=0.5,position='identity')+scale_fill_viridis_d()
b<-ggplot(d.exp_w_Points[d.exp_w_Points$subj=="diff",],aes(x=qmr,fill =subj)) + 
  geom_histogram(binwidth = 3,alpha=0.5,position='identity')+scale_fill_viridis_d()
####### Boxplots
c<-ggplot(data =d.exp_w_Points,mapping = aes(y = qmr,x = subj, fill=subj)) + geom_boxplot()+scale_fill_viridis_d()+geom_point()

d<-ggplot(data =d.exp_limit,mapping = aes(y = qmr,x = subj, fill=subj)) + geom_boxplot()+scale_fill_viridis_d()+geom_point()

ggarrange(a, b,c, d,labels = c("A","B","C","D"),
                    ncol = 2, nrow = 2)

res_w_Points<-t.test(d.exp_w_Points[d.exp_w_Points$subj=="pat",]$qmr, d.exp_w_Points[d.exp_w_Points$subj=="ctrl",]$qmr, paired = TRUE,
alternative = "two.sided", conf.level = 0.95,var.equal=TRUE)
res_wo_Points<-t.test(d.exp_limit[d.exp_limit$subj=="pat",]$qmr, d.exp_limit[d.exp_limit$subj=="ctrl",]$qmr, paired = TRUE,
alternative = "two.sided", conf.level = 0.95,var.equal=TRUE)

```

## **Trap Nr. 3**: This one looks wrong. Let's remove it
##TO DO:post-hoc data selection, Keep adjusting the data collection removing outliers, 1) use different threshold, 2) remove outliers and test till you get you result

```{r echo= FALSE}
load('Removing_values.RData')
a<-ggplot(d.exp_w_Outl,aes(x=qmr,fill =subj)) + 
  geom_histogram(binwidth = 3,alpha=0.5,position='identity')+scale_fill_viridis_d()
b<-ggplot(d.exp_w_Outl[d.exp_w_Outl$subj=="diff",],aes(x=qmr,fill =subj)) + 
  geom_histogram(binwidth = 3,alpha=0.5,position='identity')+scale_fill_viridis_d()
####### Boxplots
c<-ggplot(data =d.exp_w_Outl,mapping = aes(y = qmr,x = subj, fill=subj)) + geom_boxplot()+scale_fill_viridis_d()+geom_point()

d<-ggplot(data =d.exp,mapping = aes(y = qmr,x = subj, fill=subj)) + geom_boxplot()+scale_fill_viridis_d()+geom_point()

ggarrange(a, b,c, d,labels = c("A","B","C","D"),
                    ncol = 2, nrow = 2)

d.extra<-d.exp_w_Outl

#t.test(d.exp_limit[d.exp_limit$subj=="pat",]$qmr, d.exp_limit[d.exp_limit$subj=="ctrl",]$qmr, paired = TRUE,
#alternative = "two.sided", conf.level = 0.95,var.equal=TRUE)
 
res_wo_Outlier<-t.test(d.exp[d.exp$subj=="pat",]$qmr, d.exp[d.exp$subj=="ctrl",]$qmr, paired = FALSE,
alternative = "two.sided", conf.level = 0.95,var.equal=TRUE)

res_w_Outlier<-t.test(d.exp_w_Outl[d.exp_w_Outl$subj=="pat",]$qmr, d.exp_w_Outl[d.exp_w_Outl$subj=="ctrl",]$qmr, paired = TRUE,
alternative = "two.sided", conf.level = 0.95,var.equal=TRUE)


```


## **Trap Nr. 4**: Problem of repeated sequential testing
### Bonferroni and other corrections
```{r echo= FALSE}
library(ggplot2)# A great library for visualization
library(viridis)#For the colormap
library(ggpubr)#For multiple subplots in ggplot
library(effsize)
# Randomly choose number of samples (1000/50/25/15/5) 
#nr_s<-15
#sample_rows<-sample(nrow(iris),nr_s)
#d.subiris<-iris[sample_rows,]
load('Subiris.RData')
#Later you can also go ahead and modify all values and study the effect
#Let's assume I measured 8 different parameters
#Here we will use a default r dataset
library(datasets)
data("iris")
summary(iris)

### Boxplots
a<-ggplot(data = d.subiris,mapping = aes(y = Sepal.Length,x = Species, fill=Species)) + geom_boxplot()+scale_fill_viridis_d()+geom_point()
b<-ggplot(data = d.subiris,mapping = aes(y = Sepal.Width,x = Species, fill=Species)) + geom_boxplot()+scale_fill_viridis_d()+geom_point()
c<-ggplot(data = d.subiris,mapping = aes(y = Petal.Length,x = Species, fill= Species)) + geom_boxplot()+scale_fill_viridis_d()+geom_point()
d<-ggplot(data = d.subiris,mapping = aes(y = Petal.Width,x = Species, fill=Species)) + geom_boxplot()+scale_fill_viridis_d()+geom_point()
#######
ggarrange(a,b,c,d, labels = c("A","B","C","D"),
          ncol = 2, nrow = 2)
#cohen.d(d.exp[d.exp$subj=="pat",]$qmr, d.exp[d.exp$subj=="ctrl",]$qmr)
```
```{r echo= FALSE}
load('Subiris.RData')
#### t-test
#res.1<-t.test(d.subiris[d.subiris$Species=="setosa",]$Petal.Length, d.subiris[d.subiris$Species=="versicolor",]$Petal.Length, paired = FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
#res.2<-t.test(d.subiris[d.subiris$Species=="setosa",]$Petal.Width, d.subiris[d.subiris$Species=="versicolor",]$Petal.Width, paired = FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
#res.3<-t.test(d.subiris[d.subiris$Species=="setosa",]$Sepal.Width, d.subiris[d.subiris$Species=="versicolor",]$Sepal.Width, paired = FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
#res.4<-t.test(d.subiris[d.subiris$Species=="setosa",]$Sepal.Length, d.subiris[d.subiris$Species=="versicolor",]$Sepal.Width, paired = FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
#res.5<-t.test(d.subiris[d.subiris$Species=="setosa",]$Sepal.Length, d.subiris[d.subiris$Species=="virginica",]$Sepal.Width,paired=FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
#res.6<-t.test(d.subiris[d.subiris$Species=="setosa",]$Sepal.Length, d.subiris[d.subiris$Species=="virginica",]$Sepal.Width, paired = FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
#res.7<-t.test(d.subiris[d.subiris$Species=="setosa",]$Sepal.Length, d.subiris[d.subiris$Species=="virginica",]$Sepal.Width, paired = FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
#res.8<-t.test(d.subiris[d.subiris$Species=="setosa",]$Sepal.Length, d.subiris[d.subiris$Species=="virginica",]$Sepal.Width, paired = FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
#res.9<-t.test(d.subiris[d.subiris$Species=="versicolor",]$Sepal.Length, d.subiris[d.subiris$Species=="virginica",]$Sepal.Width, paired = FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
#res.10<-t.test(d.subiris[d.subiris$Species=="versicolor",]$Sepal.Length, d.subiris[d.subiris$Species=="virginica",]$Sepal.Width, paired = FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
#res.11<-t.test(d.subiris[d.subiris$Species=="versicolor",]$Sepal.Length, d.subiris[d.subiris$Species=="virginica",]$Sepal.Width, paired = FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
#res.12<-t.test(d.subiris[d.subiris$Species=="versicolor",]$Sepal.Length, d.subiris[d.subiris$Species=="virginica",]$Sepal.Width, paired = FALSE,
#alternative = "two.sided", conf.level = 0.95,var.equal=FALSE)
p_no_corr<-(c(res.1$p.value,res.2$p.value,res.3$p.value,res.4$p.value,res.5$p.value,res.6$p.value,res.7$p.value,res.8$p.value,res.9$p.value,res.10$p.value,res.11$p.value,res.12$p.value))
p_adjusted<-p.adjust(p_no_corr, method = "bonferroni", n = length(p_no_corr))

plot(p_no_corr,ylim=c(0,1.2))
lines(p_adjusted,lty=2)
```

## **Trap Nr. 5**: TODO POST HOC hypothesis
### Be ware of one-sided tests,

###Check the assumptions: (different variation, reaching normality)
```{r echo= FALSE}
load('Adding_values.RData')
res1<-t.test(d.exp_limit[d.exp_limit$subj=="pat",]$qmr, d.exp_limit[d.exp_limit$subj=="ctrl",]$qmr, paired = TRUE,
alternative = "two.sided", conf.level = 0.95,var.equal=TRUE)
res2<-t.test(d.exp_limit[d.exp_limit$subj=="pat",]$qmr, d.exp_limit[d.exp_limit$subj=="ctrl",]$qmr, paired = TRUE,
alternative = "less", conf.level = 0.95,var.equal=TRUE)
res3<-t.test(d.exp_limit[d.exp_limit$subj=="pat",]$qmr, d.exp_limit[d.exp_limit$subj=="ctrl",]$qmr, paired = TRUE,
alternative = "greater", conf.level = 0.95,var.equal=TRUE)

c(res1$p.value,res2$p.value,res3$p.value)

```

##References
```{r  echo=FALSE}
mybib <- RefManageR::ReadBib("pHacking.bib", check = FALSE) 
mybib


```



